%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.3 (22/9/2018)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% v1.3 author:
% Zachary Taylor
%
% v1.3 repository:
% https://github.com/ZDTaylor/Deedy-Resume-Reversed
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Add various styling and section options and allow for multiple pages smoothly.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.3:
% 1. Removed MacFonts version as I have no desire to maintain it nor access to macOS
% 2. Switched column ordering
% 3. Changed font styles/colors for easier human readability
% 4. Added, removed, and rearranged sections to reflect my own experience
% 5. Hid last updated
%
% v1.2:
% 1. Added publications in place of societies.
% 2. Collapsed a portion of education.
% 3. Fixed a bug with alignment of overflowing long last updated dates on the top right.
%
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-multilatex}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Alice Walker}{ %\urlstyle{same}\href{http://example.com}{example.com}| \href{http://example2.co}{example2.co}\\
\href{mailto:alice.walker@example.com}{alice.walker@example.com} | \href{tel:1234567890}{123.456.7890}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Tech Solutions Inc.}
\descript{| Senior Software Engineer}
\location{July 2021 – Present | San Francisco, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Led the development of a scalable microservices-based architecture for a new cloud-based platform, utilizing AWS and Python.
\item Implemented real-time data analytics and visualization using Python, Spark, and React.js, resulting in increased data insights for clients.
\item Collaborated with cross-functional teams to design and deploy a cutting-edge AI-driven chatbot system for customer support.
\item Mentored junior developers, conducting code reviews and promoting best practices, resulting in improved team productivity and code quality.
\end{tightemize}
\sectionsep

\runsubsection{CodeCrafters Co.}
\descript{| Software Engineer}
\location{Jan 2019 – June 2021 | Seattle, WA}
\begin{tightemize}
\item Developed and maintained robust backend services in Python and Django, ensuring seamless integration with frontend applications.
\item Collaborated with UX designers to create intuitive user interfaces using React.js and Redux, resulting in a 20% increase in user satisfaction.
\item Implemented automated testing practices, resulting in a significant reduction in software defects and faster deployment cycles.
\item Spearheaded a company-wide initiative to migrate legacy applications to a cloud-based infrastructure on AWS.
\end{tightemize}
\sectionsep

\runsubsection{AppStart Labs}
\descript{| Software Engineering Intern}
\location{May 2018 – Aug 2018 | Austin, TX}
\begin{tightemize}
\item Assisted in the development of a mobile application using React Native, contributing to its successful launch on both iOS and Android platforms.
\item Conducted performance testing and optimization, resulting in a 30% improvement in app loading times.
\item Collaborated with a team of developers to troubleshoot and resolve critical bugs and issues, ensuring a smooth user experience.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{AI-Powered Personal Assistant}
\descript{| Team Lead}
\location{Feb 2020 – Dec 2020 | CodeCrafters Co.}
\begin{tightemize}
\item Led a team of five developers to create an AI-powered personal assistant capable of voice-based interaction using natural language processing (NLP) algorithms.
\item Developed backend APIs using Flask and integrated NLP models to process user commands effectively.
\item Utilized Docker and Kubernetes for containerization and scalable deployment on the company's cloud infrastructure.
\end{tightemize}
\sectionsep

\runsubsection{SecureChat}
\descript{| Open Source Project}
\location{Sep 2017 – May 2018 | GitHub}
\begin{tightemize}
\item Contributed to \textbf{\href{https://github.com/SecureChat/SecureChat}{SecureChat}}, an end-to-end encrypted chat application, enhancing its security features and improving performance.
\item Collaborated with the open-source community to resolve issues and merge pull requests for a more stable application.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{University of XYZ}
\descript{Master of Science in Computer Science}
\location{May 2018 | Austin, TX}
% College of Engineering \\
\location{GPA: 3.8 / 4.0}
\sectionsep

\subsection{State University}
\descript{Bachelor of Science in Computer Science}
\location{May 2016 | Anytown, USA}
\location{GPA: 3.9 / 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{5+ years:}
Python \textbullet{} JavaScript \\
\location{3+ years:}
C/C++ \textbullet{} Java \\
\location{2+ years:}
React.js \textbullet{} Django \\
\location{1+ years:}
Flask \textbullet{} Angular \\
\sectionsep

\subsection{Technology}
Git/Github \textbullet{} AWS \textbullet{} Docker \\
Kubernetes \textbullet{} Linux \textbullet{} SQL \\
Machine Learning \textbullet{} NLP \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Machine Learning \\
Natural Language Processing \\
Big Data Analytics \\
\sectionsep

\subsection{Undergraduate}
Data Structures and Algorithms \\
Database Systems \\
Operating Systems \\
Artificial Intelligence \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Societies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies}
Association of Software Engineers (ASE)\\
Women in Tech (WiT)\\
Phi Beta Delta (Honor Society)\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/YourUsername}{\bf YourUsername} \\
LinkedIn://  \href{https://www.linkedin.com/in/your-325-name}{\bf your-325-name} \\
Portfolio:// \href{https://your-portfolio-website.com}{\bf your-portfolio-website}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
